---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)

```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
 
mack_creek_lengths <- mack_creek_vertebrates %>%   # Create a variable
  clean_names() %>% # Clean the names
  select(year:sampledate) %>%  # Selecting columns year:sampledate
  filter(section == "CC") %>%  #
  mutate(across(where(is.character, tolower))) %>%  # makes observation strings to lowercase
  drop_na(species) %>% #drops the NAs in species
  group_by(species) %>% # groups by the species
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
# Reprex 1 
library(reprex)
library(datapasta)

my_data <- data.frame(
  stringsAsFactors = FALSE,
              YEAR = c(1987, 1987, 1987, 1987, 1987),
          SITECODE = c("MACKCC-L","MACKCC-L",
                       "MACKCC-L","MACKCC-L","MACKCC-L"),
           SECTION = c("CC", "CC", "CC", "CC", "CC"),
             REACH = c("L", "L", "L", "L", "L"),
              PASS = c(1, 1, 1, 1, 1),
           UNITNUM = c(1, 1, 1, 1, 1),
          UNITTYPE = c("R", "R", "R", "R", "R"),
        VERT_INDEX = c(1, 2, 3, 4, 5),
         PITNUMBER = c(NA, NA, NA, NA, NA),
           SPECIES = c("ONCL", "ONCL", "ONCL", "ONCL", "ONCL"),
           LENGTH1 = c(58, 61, 89, 58, 93),
           LENGTH2 = c(NA, NA, NA, NA, NA),
            WEIGHT = c(1.75, 1.95, 5.6, 2.15, 6.9),
              CLIP = c("NONE", "NONE", "NONE", "NONE", "NONE"),
        SAMPLEDATE = c("10/7/87", "10/7/87", "10/7/87", "10/7/87", "10/7/87")
)
  
mack_creek_lengths <- mack_creek_vertebrates %>%   # Create a variable
  clean_names() %>% # Clean the names
  select(year:sampledate) %>%  # Selecting columns year:sampledate
  filter(section == "CC") %>%  #
  mutate(across(where(is.character, tolower))) %>%  # makes observation strings to lowercase
  drop_na(species) %>% #drops the NAs in species
  group_by(species) %>% # groups by the species
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()

```


```{r}

```

### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

## End